---
title: "Absolute basics of R, RStudio, RStudio Cloud, Git, and GitHub"
output: html_document
---

## Create folder stucture, load packages, objects and functions
```{r}
# remove any potential lingering objects and data from RStudio when running a new script
rm(list=ls())

# 1a Declare root directory, folder locations and load essential stuff
project.folder <- paste0(here::here(),'/')
source(paste0(project.folder,'create_folder_structure.R'))
source(paste0(essentials.folder,'a_04_script_initiate.R'))
```

## What is R?

R is an interactive environment developed by statisticians for data analysis.\
A more detailed Introduction to R can be found at https://www.r-project.org. \
This guide assumes the user has functional knowledge of R.\
The code below will provide details of which R Version is currently being used.
```{r}
# which R version am I using?
print(R.Version())
```

Plot something in R
```{r}
set.seed(1)
x=rnorm(100); y = rnorm(100)
plot(x,y)
```

## What is RStudio?

RStudio is an integrated development environment (IDE) for R developed by J J Allaire.\
RStudio provides a convenient graphical interface to R, making it more user-friendly, and providing many useful features.\
Such features include direct code execution, tools for plotting, history, debugging and workspace management.\
This guide assumes the user has functional knowledge of RStudio.\
A more detailed background on to RStudio can be found at https://www.rstudio.com/about/. \
The code below will provide details of which RStudio Version is currently being used.\
```{r}
print(rstudioapi::versionInfo())
```

## What is RStudio Cloud?

RStudio Cloud is a cloud-based RStudio which runs projects and code "in the cloud".\
RStudio Cloud allows convenient scaling and sharing of code, including for training programs such as SHARP.\
Registration for free is available via https://rstudio.cloud/\
More details are available via https://rstudio.cloud/learn/guide
```{r}
# TO DO
```

## What is Git?
```{r}
# TO DO
```

## What is GitHub?
```{r}
# TO DO
```