---
title: "Run some basic R"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Remove any potential lingering objects and data from RStudio when running a new script
```{r}
rm(list=ls())
```

## Which R version am I using?
```{r}
print(R.Version())
```

## Plot something

### Plot something using R base functionality
```{r}
set.seed(1)
x <- rnorm(100); y = rnorm(100)
plot(x,y)
```

### Plot something in R using ggplot
```{r}
data <- data.frame(x,y)

library(ggplot2)

ggplot(data) + 
  geom_point(aes(x=x,y=y)) +
  xlab('x-axis label') + ylab('y-axis label') +
  theme_classic()

data <- NULL
```

## Create numerical objects and make some simple operational manipulations and tests

### Create two numerical objects, a and b
```{r}
a <- 11
b <- 6
```

### Addition of a and b
```{r}
a+b
```

### Subtraction of a and b
```{r}
a-b
```

### Multiplication of a and b
```{r}
a*b
```

### Division of a and b
```{r}
a/b
```

### Modulus (remainder of division) of a and b
```{r}
a%%b
```

### Raise a to the power of b
```{r}
a^b
```

### Is a less than b?
```{r}
a<b
```

### Is b less than a?
```{r}
b<a
```

### Is a equal to b?
```{r}
a == b
```

### Is a not equal to b?
```{r}
a!=b
```

## Create a vector and make simple manipulations

### Create vector_1
```{r}
vector_1 <- c(6,7,8,9,10)
```

### Print how many elements vector_1 has
```{r}
length(vector_1)
```

### Third element of vector_1
```{r}
vector_1[3]
```

### Second and fourth element of vector_1
```{r}
vector_1[c(2,4)]
```

### Access all but first element of vector_1
```{r}
vector_1[-1]
```

### Take elements of vector_1 less than 9
```{r}
vector_1[vector_1<9]
```

### Modify vector_1 2nd element
```{r}
vector_1[2] <- -1
vector_1
```

### Modify vector elements less than 9 to be -1
```{r}
vector_1[vector_1 < 9] <- -1 
vector_1
```

### Truncate vector_1 first four elements
```{r}
vector_1 <- vector_1[1:4]
vector_1
```

### Delete vector_1
```{r}
vector_1 <- NULL
```

### Add two vectors together
```{r}
vector_1 <- c(6,7,8,9,10)
vector_2 <- c(11,12,13,14,15)
vector_3 <- vector_1 + vector_2
vector_3
```

### Multiply two vectors together
```{r}
vector_4 <- vector_1 * vector_2
vector_4
```

## Using 'which' function for a vector to find elements of vector
```{r}
vector_4_elements <- which(vector_4 < 100)
vector_4_elements
vector_4[vector_4_elements]
```

## Create and index a matrix

### Create matrix_1
```{r}
matrix_1_data <- c(1,2,3,4,5,6,7,8,9) 
matrix_1 <- matrix(matrix_1_data,nrow=3,ncol=3,byrow=TRUE)
matrix_1
```

### Print how many elements matrix_1 has
```{r}
length(matrix_1)
```

### Dimensions of matrix_1
```{r}
dim(matrix_1)
```

### Third element of second row
```{r}
matrix_1[2,3]
```

### Delete matrix_1
```{r}
matrix_1 <- NULL
```

### Add two matrices together
```{r}
matrix_1_data <- c(1,2,3,4,5,6,7,8,9) 
matrix_1 <- matrix(matrix_1_data,nrow=3,ncol=3,byrow=TRUE)

matrix_2_data <- c(11,12,13,14,15,16,17,18,19) 
matrix_2 <- matrix(matrix_2_data,nrow=3,ncol=3,byrow=TRUE)

matrix_3 <- matrix_1 + matrix_2
matrix_3
```

### Multiply two matrices together
```{r}
matrix_4 <- matrix_1 %*% matrix_2
matrix_4
```

## Create a function and use it

### Formula to convert celsius to fahrenheit
```{r}
temp_Fahrenheit = 32
temp_Celsius <- (temp_Fahrenheit - 32) * 5 / 9
temp_Celsius
```

### Define function to convert celsius to fahrenheit
```{r}
fahrenheit_to_celsius <- function(temp_F) {
  temp_C <- (temp_F - 32) * 5 / 9
  return(temp_C)
}
```

### Use function above to convert 
```{r}
fahrenheit_to_celsius(5)
```

### Farhrenheit and celsius are the same at -40
```{r}
fahrenheit_to_celsius(-40)
```
